Revisions

### 2024-08-27 revisions.qmd
tweaks

---
title: Revisions
author:
- name: Thomas E. Gorman
  url: https://tegorman13.github.io/
page-layout: full
toc: true
format:
  html: default
  gfm: default
  docx:
    prefer-html: true
    output-file: "tg_revisions.docx"
    toc: false
---

>>>>

---
title: Revisions
author:
- name: Thomas E. Gorman
  url: https://tegorman13.github.io/
page-layout: full
toc: true
suppress-bibliography: true
format:
  html: default
  gfm: default
  docx:
    prefer-html: true
    output-file: "tg_revisions.docx"
    toc: false
---
